Race to the Ballot Box: Will Demographics Decide a Winner This Year?

### 2024-11-01 paper/paper.qmd
Updating the table in the paper

set.seed(12)
data <- read_parquet("../data/analysis_data/analysis_data.parquet")
model <- readRDS("../models/election_model.rds")
training_index <- createDataPartition(data$candidate_trump, p = 0.7, list = FALSE)
testing_data <- data[-training_index,]

testing_data |>
  select(pollster, state, candidate_trump, pct) |>
  mutate(
    state = recode(state, "Maine CD-1" = "Maine", 
                          "Maine CD-2" = "Maine",
                          "Nebraska CD-2" = "Nebraska"),
    predicted_pct = 100 * posterior_predict(model, newdata = testing_data, 
                                                  draws = 2000, type = "response") |> colMeans(),
    winner_trump = ifelse(predicted_pct > 50, 1, 0)
  ) |>
  group_by(state) |> 
  summarise(predicted_prob = round(mean(predicted_pct), 2), .groups = "drop") |>
  left_join(electoral_votes, by = c("state" = "state")) |>
  mutate(predicted_winner = ifelse(predicted_prob > 50, "Trump", "Harris")) |>
  kbl(booktabs = TRUE, col.names = c("State", "Predicted Trump %", "Electoral Votes", "Predicted Winner"))
```

>>>>

predicted_data <- read_parquet("../data/analysis_data/predicted_data.parquet")

predicted_data_trump <- predicted_data |>
  filter(candidate_trump == 1) |>
  select(state, pct, predicted_pct_trump) |>
  mutate(state = recode(state, "Maine CD-1" = "Maine", "Maine CD-2" = "Maine",
                        "Nebraska CD-2" = "Nebraska")) |>
  group_by(state) |>
  summarise(predicted_pct_trump = round(mean(predicted_pct_trump), 2))

predicted_data_harris <- predicted_data |>
  filter(candidate_harris == 1) |>
  select(state, pct, predicted_pct_harris) |>
  mutate(state = recode(state, "Maine CD-1" = "Maine", "Maine CD-2" = "Maine",
                        "Nebraska CD-2" = "Nebraska")) |>
  group_by(state) |>
  summarise(predicted_pct_harris = round(mean(predicted_pct_harris), 2))

predicted_data_harris |> 
  merge(predicted_data_trump, all = T) |>
  left_join(electoral_votes, by = c("state" = "state")) |>
  mutate(predicted_winner = ifelse(replace_na(predicted_pct_harris, 50) <
                                     replace_na(predicted_pct_trump, 50), 
                                   "Trump", "Harris")) |>
  kbl(booktabs = TRUE, col.names = c("State", "Predicted Harris %", "Predicted Trump %", "Electoral Votes", "Predicted Winner"))
```
